The one characterizing the parental care stages

### 2019-10-11 analysis/07_hormones.Rmd
new hormone fig

a <- hormonecharplot("prolactin", "PRL (ng/mL)")
b <- hormonecharplot("cort", "CORT (ng/mL)")
c <- hormonecharplot("progesterone", "PROG (ng/mL)") 
d1 <- hormonecharplot("estradiol", "E (ng/mL)")
d2 <- hormonecharplot("testosterone", "T (ng/mL)")
d <- plot_grid(d1,d2, nrow = 1)
abcd <- plot_grid(a, b ,c, d)
mylegend <- get_legend(c + theme(legend.position = "bottom"))
plot_grid(abcd, mylegend, nrow = 2, rel_heights = c(0.85,0.15))
```

>>>>

a <- hormonecharplot("prolactin", "PRL (ng/mL)")
b <- hormonecharplot("cort", "CORT (ng/mL)")
c <- hormonecharplot("progesterone", "PROG (ng/mL)") 
d1 <- hormonecharplot("estradiol", "E (ng/mL)")
d2 <- hormonecharplot("testosterone", "T (ng/mL)")
d <- plot_grid(d1,d2, nrow = 1)
abcd <- plot_grid(a, b ,c, d, labels = "AUTO")
mylegend <- get_legend(c + theme(legend.position = "bottom"))
plot_grid(abcd, mylegend, nrow = 2, rel_heights = c(0.85,0.15))
```

### 2019-10-11 docs/ms1-charactization.Rmd
new colors
new hormone fig

---
title: "The one characterizing the parental care stages"
output: word_document
author:
- Principal Investigators - Rebecca Calisi, Matt MacManes, John Wingfield
- Postdocs - Suzanne Austin, Rayna Harris, Jesse Krause, 
- Grad students - Victoria Farrar, April Booth, Andrew Lang
- Undergrads - Tanner Feustel, Candice Lee, Annie Bond?
- Others - Fred?, Rechelle Viernes
---

@@

## Fig 2: circulating prolactin peaks at hatch in M and F

@@

### Fig 2 supplement. CORT but not E,T, or P respond significantly to treatment

![](../figures/hormones/characterization-2.png)

>>>>

---
title: "The one characterizing the parental care stages"
output: md_document
author:
- Principal Investigators - Rebecca Calisi, Matt MacManes, John Wingfield
- Postdocs - Suzanne Austin, Rayna Harris, Jesse Krause, 
- Grad students - Victoria Farrar, April Booth, Andrew Lang
- Undergrads - Tanner Feustel, Candice Lee, Annie Bond?
- Others - Fred?, Rechelle Viernes
---

@@

## Fig 2: hormones

@@
